An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-12 scagnostics.Rmd
Fixed Fig 5.

```{r plannedtourpath}
if(!file.exists("cache/plannedtourpath.rda")){
  m1 <- matrix(c(1,0,0,0,0,0,0,1,0,0,0,0),ncol=2)
  m2 <- matrix(c(0,0,0,0,1,0,0,0,0,0,0,1),ncol=2)
  #this is silly but seems that first two entries are being ignored, so need some fake entries
  m3 <- matrix(c(1,0,0,0,1,0,0,1,0,0,0,1),ncol=2)
  m4 <- matrix(c(1,1,1,0,0,0,0,1,1,0,0,0),ncol=2)
  t2 <- save_history(sin100,tour_path=planned_tour(list(m3,m4,m1,m2)))
  t2full <- as.list(interpolate(t2))
  fullResPlanned <- getProj(sin100, t2full, "sin", 100) %>%
    rbind(getProj(sin1000, t2full, "sin", 1000)) %>%
    rbind(getProj(sphere100, t2full, "sphere", 100)) %>%
    rbind(getProj(sphere1000, t2full, "sphere", 1000)) %>%
    rbind(getProj(pipe100, t2full, "pipe", 100)) %>%
    rbind(getProj(pipe1000, t2full, "pipe", 1000)) %>%
    rbind(getProj(sin100S, t1full, "sin-S", 100)) %>%
    rbind(getProj(sin1000S, t1full, "sin-S", 1000)) %>%
    rbind(getProj(sphere100S, t1full, "sphere-S", 100)) %>%
    rbind(getProj(sphere1000S, t1full, "sphere-S", 1000)) %>%
    rbind(getProj(pipe100S, t1full, "pipe-S", 100)) %>%
    rbind(getProj(pipe1000S, t1full, "pipe-S", 1000))
  save(t2, t2full, fullResPlanned, file = "cache/plannedtourpath.rda")
} else {
  load("cache/plannedtourpath.rda")
}
```

```{r plannedtour, fig.width=6, fig.height=7, fig.cap="As Figure \ref{fig:plotV1V2toV3V4} but moving from the projection onto V1-V2 to the projection onto V5-V6, i.e. starting from random distribution view, and moving into the special view."}
fullResMeltPlanned <- melt(fullResPlanned, id=c("t", "name", "size")) %>%
  mutate(sphered = str_detect(name,"-")) %>%
  mutate(name=str_replace(name,"-S",""))
ggplot(fullResMeltPlanned, aes(x=t, y=value)) +
  geom_line(aes(color=factor(size),linetype = factor(sphered))) + 
  facet_wrap(variable~name, ncol=3, scales = "free_y", labeller = label_wrap_gen(multi_line=FALSE)) +
  guides(color=FALSE)
```

>>>>

```{r plannedtourpath}
if(!file.exists("cache/plannedtourpath.rda")){
  m1 <- matrix(c(1,0,0,0,0,0,0,1,0,0,0,0),ncol=2)
  m2 <- matrix(c(0,0,0,0,1,0,0,0,0,0,0,1),ncol=2)
  #this is silly but seems that first two entries are being ignored, so need some fake entries
  m3 <- matrix(c(1,0,0,0,1,0,0,1,0,0,0,1),ncol=2)
  m4 <- matrix(c(1,1,1,0,0,0,0,1,1,0,0,0),ncol=2)
  t2 <- save_history(sin100,tour_path=planned_tour(list(m3,m4,m1,m2)))
  t2full <- as.list(interpolate(t2))
  fullResPlanned <- getProj(sin100, t2full, "sin", 100) %>%
    rbind(getProj(sin1000, t2full, "sin", 1000)) %>%
    rbind(getProj(sphere100, t2full, "sphere", 100)) %>%
    rbind(getProj(sphere1000, t2full, "sphere", 1000)) %>%
    rbind(getProj(pipe100, t2full, "pipe", 100)) %>%
    rbind(getProj(pipe1000, t2full, "pipe", 1000)) %>%
    rbind(getProj(sin100S, t2full, "sin-S", 100)) %>%
    rbind(getProj(sin1000S, t2full, "sin-S", 1000)) %>%
    rbind(getProj(sphere100S, t2full, "sphere-S", 100)) %>%
    rbind(getProj(sphere1000S, t2full, "sphere-S", 1000)) %>%
    rbind(getProj(pipe100S, t2full, "pipe-S", 100)) %>%
    rbind(getProj(pipe1000S, t2full, "pipe-S", 1000))
  save(t2, t2full, fullResPlanned, file = "cache/plannedtourpath.rda")
} else {
  load("cache/plannedtourpath.rda")
}
```

```{r plannedtour, fig.width=6, fig.height=7, fig.cap="As Figure \\ref{fig:plotV1V2toV3V4} but moving from the projection onto V1-V2 to the projection onto V5-V6, i.e. starting from random distribution view, and moving into the special view."}
fullResMeltPlanned <- melt(fullResPlanned, id=c("t", "name", "size")) %>%
  mutate(sphered = str_detect(name,"-")) %>%
  mutate(name=str_replace(name,"-S",""))
ggplot(fullResMeltPlanned, aes(x=t, y=value)) +
  geom_line(aes(color=factor(size),linetype = factor(sphered))) + 
  facet_wrap(variable~name, ncol=3, scales = "free_y", labeller = label_wrap_gen(multi_line=FALSE)) +
  guides(color=FALSE)
```
